Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Fix up figure for labelless nodes in state graphs.
Trying to get state graphs drawn closer to scale.
Cut code, present VS benchmark.

\begin{figure}[t]
\begin{center}
\includegraphics[width=2.5in]{rel-time-church.ps}
\end{center}
\caption{Relative run-time of
optimized analyzers to baseline for Church numeral example.}
\label{fig:churchtime}
\end{figure}

@@

\newcommand{\church}[1]{\(\ulcorner{\tt #1}\urcorner\)}
\begin{figure}
\hrule
\vspace{2mm}
\begin{alltt}
(define (zero? n) ((n (\(\lambda\) (zx) #f)) #t))
(define (((mult m1) m2) mf) (m2 (m1 mf)))
(define ((((plus p1) p2) pf) x)
  ((p1 pf) ((p2 pf) x)))

(define (((pred n) rf) rx)
  (((n (\(\lambda\) (g) (\(\lambda\) (h) (h (g rf)))))
    (\(\lambda\) (ignored) rx))
   (\(\lambda\) (id) id)))

(define ((church=? e1) e2)
  (if (zero? e1) (zero? e2)
      (if (zero? e2) #f
          ((church=? (pred e1)) (pred e2)))))

;; multiplication distributes over addition
((church=? ((mult \church2) ((plus \church1) \church3)))
 ((plus ((mult \church2) \church1)) ((mult \church2) \church3)))
\end{alltt}
\caption{Church-numeral calculation}
\label{fig:church}
\end{figure}

\begin{figure}[t]
\hrule
\vspace{2mm}
\begin{alltt}
(define (id x) x)
(define (f n)
  (if (<= n 1) 1 (* n (f (- n 1)))))
(define (g n)
  (if (<= n 1) 1 (+ (* n n) (g (- n 1)))))
(print (+ ((id f) 3) ((id g) 4)))
\end{alltt}
\hrule
\begin{center}
\begin{tabular}{ccc}
\raisebox{1ex-\height}{
\includegraphics[height=4in]{introspective-base.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=3.7in]{introspective-lazy.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=2.2in]{introspective-lazyc.pdf}}
\\
(a) Baseline
&
(b) Lazy
&
(c) Compiled (\& lazy)
\end{tabular}
\end{center}
\caption{Example state graphs for the program above.  Part (a) shows
  the result of the baseline analyzer.  It has long ``corridor''
  transitions and ``diamond'' subgraphs that fan-out from
  nondeterminism and fan-in from joins.  Part (b) shows the result of
  performing nondeterminism lazily and thus avoids many of the diamond
  subgraphs.  Part (c) shows the result of abstract compilation that
  removes intepretive overhead in the form of intermediate states,
  thus minimizing the corridor transitions.  The end result is a more
  compact abstraction of the program that can be generated faster.}
\label{fig:state-graphs}
\end{figure}

@@

\newpage
\section{An abstract$^{\text 2}$ machine for ISWIM}
\label{sec:aam}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Relative improvements over the baseline analyzer for the
  Vardoulakis and Shivers benchmark in terms of peak memory usage, the
  rate of state transitions, and total analysis time.}
\label{fig:churchtime}
\end{figure}

@@

%% \newcommand{\church}[1]{\(\ulcorner{\tt #1}\urcorner\)}
%% \begin{figure}
%% \hrule
%% \vspace{2mm}
%% \begin{alltt}
%% (define (zero? n) ((n (\(\lambda\) (zx) #f)) #t))
%% (define (((mult m1) m2) mf) (m2 (m1 mf)))
%% (define ((((plus p1) p2) pf) x)
%%   ((p1 pf) ((p2 pf) x)))

%% (define (((pred n) rf) rx)
%%   (((n (\(\lambda\) (g) (\(\lambda\) (h) (h (g rf)))))
%%     (\(\lambda\) (ignored) rx))
%%    (\(\lambda\) (id) id)))

%% (define ((church=? e1) e2)
%%   (if (zero? e1) (zero? e2)
%%       (if (zero? e2) #f
%%           ((church=? (pred e1)) (pred e2)))))

%% ;; multiplication distributes over addition
%% ((church=? ((mult \church2) ((plus \church1) \church3)))
%%  ((plus ((mult \church2) \church1)) ((mult \church2) \church3)))
%% \end{alltt}
%% \caption{Church-numeral calculation}
%% \label{fig:church}
%% \end{figure}

\begin{figure}[t]
%% \hrule
%% \vspace{2mm}
%% \begin{alltt}
%% (define (id x) x)
%% (define (f n)
%%   (if (<= n 1) 1 (* n (f (- n 1)))))
%% (define (g n)
%%   (if (<= n 1) 1 (+ (* n n) (g (- n 1)))))
%% (print (+ ((id f) 3) ((id g) 4)))
%% \end{alltt}
%% \hrule
\begin{center}
\begin{tabular}{ccc}
\raisebox{1ex-\height}{
\includegraphics[height=3.5in]{introspective-base.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=3.5in]{introspective-lazy.pdf}}
&
\raisebox{1ex-\height}{
\includegraphics[height=3in]{introspective-lazyc.pdf}}
\\
(a) Baseline
&
(b) Lazy
&
(c) Compiled (\& lazy)
\end{tabular}
\end{center}
\caption{Example state graphs for the program above.  Part (a) shows
  the result of the baseline analyzer.  It has long ``corridor''
  transitions and ``diamond'' subgraphs that fan-out from
  nondeterminism and fan-in from joins.  Part (b) shows the result of
  performing nondeterminism lazily and thus avoids many of the diamond
  subgraphs.  Part (c) shows the result of abstract compilation that
  removes intepretive overhead in the form of intermediate states,
  thus minimizing the corridor transitions.  The end result is a more
  compact abstraction of the program that can be generated faster.}
\label{fig:state-graphs}
\end{figure}

@@

%\newpage
\section{An abstract$^{\text 2}$ machine for ISWIM}
\label{sec:aam}
